Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-08-13 Response to reviewers.tex

\noindent This paper applies some machine learning technologies to address issues related to book sales. There are some revisions that should be addressed by authors:\\

\noindent (1) The ANN and ELM (extreme learning machine) should be added into the experiments;\\

\noindent (2) The authors should clarify their main contributions in the introduction parts.\\

\begin{verbatim}
We have rewritten the introduction and introduced this new text:

Our main contribution is, thus, to develop a
methodology to process book sales data in order to first find out
relevant variables and then use these variables to process data so
that the publisher, using them, can estimate sales and from them order
a specific print run, instead of standard ones, which are around 300
copies for standard books and around 5000 for those that are
considered, in advance, {\em best sellers}.

Also, in the next-to-last paragraph, we have laid out our methodology and the main contributions of this paper.

\end{verbatim}

### 2016-08-20 paper.tex
Added MLP results to all tables
Added methodology diagram for issue #48. Please @pacastillo or @amorag check if it is correct or if I should modify anything
moving sub-sections 4.1 and 4.2 to the Section 2 (comment 2 by Rev.3): Closes #47

@@

There is not a standard methodology to solve the general problem of sales forecasting. However, the steps we have followed in this paper are those usually applied in a Knowledge Discovery in Databases (KDD) process \cite{fayyad1996data}. %These are described in the following sections.

@@

Next, Section \ref{subsec:select_method} reports a selection of the best forecasting techniques that have been conducted, looking for those rule- or tree-based, together with numerical methods which could yield the best results.

@@

%-------------------------------------------------
%\subsection{Data collection}
%\label{subsec:data_collection}

@@

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those
regions, or clusters, with high training sample concentration and fewer
where the samples are scarce. U-Matrix graph, together with the projection of variables into separate planes, the so-called component planes analysis (that SOM yields), will aid an expert to identify the most relevant features on every cluster, i.e. those with a higher influence on the creation of that cluster.
%FERGU: mencionarlo en la intro
% Which is interesting because... JJ
% Antonio - explained. ;)

@@

Thus, in this research five forecasting methods, based on the State of the Art literature 
review (see Section \ref{sec:soa}) 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool have been chosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using
these methods. % Why these and not others? Exploratory data analysis?
               % - JJ

Specifically, the following forecasting methods are proposed: 
        % Proposed why? - JJ
        % because those methods were those that could lead with the problem data - pedro
\begin{itemize}

\subsection{Models evaluation}

@@

% An intro should go here - JJ
% Antonio - done

@@

\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  &  \textbf{89.0 $\pm$ 0.09}  &  \textbf{214.37 $\pm$ 22.96}  &  \textbf{634.23 $\pm$ 307.76}  &  \textbf{37.46 $\pm$ 3.12}  &  \textbf{48.32 $\pm$ 25.16} & 18.85 $\pm$ 0.61\tabularnewline
\hline 
kNN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  &  \textbf{0.001 $\pm$ 0.01}\tabularnewline
\hline 
RF & 84.0 $\pm$ 0.05  & 253.37 $\pm$ 29.43  & 788.94 $\pm$ 282.01  & 44.16 $\pm$ 2.76  & 57.77 $\pm$ 8.15  & 4.91 $\pm$ 0.12\tabularnewline
\hline 
LR & 87.2 $\pm$ 0.07  & 308.68 $\pm$ 25.44  & 680.91 $\pm$ 226.41  & 54.05 $\pm$ 4.38  & 52.13 $\pm$ 18.29  & 984.68 $\pm$ 128.21\tabularnewline
\hline 
SVM  & 87.6 $\pm$ 0.04  & 248.76 $\pm$ 27.49  & 732.64 $\pm$ 260.56  & 43.37 $\pm$ 2.35  & 53.47 $\pm$ 6.29  & 6169.24 $\pm$ 281.49\tabularnewline
\hline 
\end{tabular}
}
\end{table*}

@@

\begin{table*}
\centering{}%
\caption{Predicting Total sales for all publishers based on features selected
by each method. Best values in bold.
\label{tab:results_all_publishers_fs}}
% RELIEFATTRIBUTEEVAL
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
\hline 
kNN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
\hline 
RF &  \textbf{91.0 $\pm$0.05} &  \textbf{198.16 $\pm$19.50} &  \textbf{589.35 $\pm$195.80} &  \textbf{34.61 $\pm$2.27} &  \textbf{44.21 $\pm$11.63} & 3.63 $\pm$0.20\\
\hline 
LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
\hline 
SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
\hline 
\end{tabular}
}
% CFSSUBEVAL
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
\hline
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
\hline 
kNN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
\hline 
RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
\hline 
LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
\hline 
SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
\hline
\end{tabular}
}
% SOM
\centering{}% SOM
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{SOM}}\tabularnewline
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  & 86.6 $\pm$0.10  & 234.09 $\pm$23.19  & 699.56 $\pm$317.20  & 40.92 $\pm$3.25  & 53.70 $\pm$26.87  & 0.475 $\pm$0.12\tabularnewline
\hline 
kNN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  &  \textbf{0.001 $\pm$0.004}\tabularnewline
\hline 
RF &  \textbf{89.8 $\pm$0.05}  &  \textbf{211.87 $\pm$20.07}  &  \textbf{617.78 $\pm$187.16}  &  \textbf{37.02 $\pm$2.46}  &  \textbf{46.58 $\pm$11.14}  & 2.93 $\pm$0.11\tabularnewline
\hline 
LR  & 85.5 $\pm$0.08  & 351.99 $\pm$23.72  & 714.76 $\pm$214.21  & 61.65 $\pm$4.28  & 54.67 $\pm$16.88  & 0.01 $\pm$0.01\tabularnewline
\hline 
SVM  & 84.5 $\pm$0.04  & 267.71 $\pm$33.82  & 888.33 $\pm$308.93  & 46.60 $\pm$2.87  & 64.62 $\pm$5.45  & 32.27 $\pm$4.74\tabularnewline
\hline 
\end{tabular}
}
\end{table*}

@@

\begin{table*}
\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company). Best values in bold. }
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  &  \textbf{90.0 $\pm$0.10} &  \textbf{670.24 $\pm$181.05}  &  \textbf{1065.34 $\pm$413.84}  &  \textbf{40.83 $\pm$10.86}  &  \textbf{43.56 $\pm$19.87}  & 0.03 $\pm$0.002\tabularnewline
\hline 
kNN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  &  \textbf{0 $\pm$0.0001}\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case1results}
\end{table*}

\begin{table*}
\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company). Best values in bold. }
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
kNN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
\hline 
RF &  \textbf{85.8 $\pm$0.17}  & 14.19 $\pm$6.69  &  \textbf{23.57 $\pm$11.83}  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  &  \textbf{14.01 $\pm$7.61}  & 25.61 $\pm$15.30  &  \textbf{40.66 $\pm$16.03}  &  \textbf{53.28 $\pm$18.45}  & 0.02 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case2results}
\end{table*}

\begin{table*}
\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  &  \textbf{88.9 $\pm$0.07} &  \textbf{71.26 $\pm$21.29}  &  \textbf{125.19 $\pm$50.09}  &  \textbf{39.25 $\pm$11.77}  &  \textbf{47.50 $\pm$15.93}  & 0.05 $\pm$0.03\tabularnewline
\hline 
kNN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case3results}
\end{table*}

\begin{table*}
\caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold)). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
kNN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  &  \textbf{0 $\pm$0.0002}\tabularnewline
\hline 
RF &  \textbf{86.7 $\pm$0.07}  &  \textbf{449.16 $\pm$127.80}  &  \textbf{671.76 $\pm$212.74}  &  \textbf{45.58 $\pm$9.80}  &  \textbf{51.37 $\pm$11.16}  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case4results}
\end{table*}

>>>>

% following two sub-sections have been moved here as requested by reviewer #3 in comment #2 (issue #47)

Thus, in this research five forecasting methods, based on the State of the Art 
literature review (see above, Section \ref{sec:soa}) 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, 
have been used. 
Well known forecasting methods implemented in the Weka tool have been chosen, 
as these methods are widely known, and could be very helpful for practitioners 
to reproduce experiments and even to solve similar sales prediction problems 
using these methods.

Specifically, the following forecasting methods are proposed:

\begin{itemize}

 % weka.classifiers.functions.MultilayerPerceptron
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
 \item \emph{Multilayer Perceptron}:
A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
artificial neural network model that maps the input data onto an appropriate output. 
It is an artificial neural network generally used for classification or 
approximation problems.

This model is a generalisation of the standard linear perceptron that uses several 
layers of nodes (called neurons) and that is able to solve linearly inseparable 
problems \cite{SteinwenderBitzer2003}.
Each neuron consists of a linear combination of weighted inputs which is passed 
though a non-linear activation function to produce its output.

This kind of artificial neural network is trained using a supervised learning 
technique called back-propagation.
This training method was developed independently by Werbos \cite{Werbos1974}, 
Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
in updating the weights of the output layer neurons once the erroneous output 
has been obtained, and then, propagating the successive weight layers back to 
the input layer.

A key issue when designing an MLP is the number of hidden layers of neurons.
Lippmann proved in \cite{Lippmann1987} that two hidden layers are enough to 
create classifying regions of any kind. This result was then confirmed in later 
works by Bishop \cite{Bishop1996} and Reed et al. \cite{Reed1999}.

%-------------------------------------------------
\subsection{Models evaluation}
\label{subsec:models_evaluation}

% previous two sub-sections have been moved here as requested by reviewer #3 in comment #2 (issue #47)

@@

There is not a standard methodology to solve the general problem of sales forecasting. However, the steps we have followed in this paper are those usually applied in a Knowledge Discovery in Databases (KDD) process \cite{fayyad1996data}. Figure \ref{fig:methodology} summarizes these followed steps.

\begin{figure}[!ht] 
\begin{center}
  \epsfig{file=metodologia.eps,width=4cm}
\caption{Steps followed in the proposed methodology.}
\label{fig:methodology}
\end{center}
\end{figure}

%These are described in the following sections.

@@

In Section \ref{subsec:select_method}, a selection of the best forecasting techniques that have been conducted has been reported, looking for those rule- or tree-based, together with numerical methods which could yield the best results.

@@

@@

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those
regions, or clusters, with high training sample concentration and fewer
where the samples are scarce. U-Matrix graph, together with the projection 
of variables into separate planes, the so-called component planes analysis 
(that SOM yields), will aid an expert to identify the most relevant features 
on every cluster, i.e. those with a higher influence on the creation of that 
cluster.

@@

@@

@@

\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  &  \textbf{89.0 $\pm$ 0.09}  &  \textbf{214.37 $\pm$ 22.96}  &  \textbf{634.23 $\pm$ 307.76}  &  \textbf{37.46 $\pm$ 3.12}  &  \textbf{48.32 $\pm$ 25.16} & 18.85 $\pm$ 0.61\tabularnewline
\hline 
kNN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  &  \textbf{0.001 $\pm$ 0.01}\tabularnewline
\hline 
RF & 84.0 $\pm$ 0.05  & 253.37 $\pm$ 29.43  & 788.94 $\pm$ 282.01  & 44.16 $\pm$ 2.76  & 57.77 $\pm$ 8.15  & 4.91 $\pm$ 0.12\tabularnewline
\hline 
LR & 87.2 $\pm$ 0.07  & 308.68 $\pm$ 25.44  & 680.91 $\pm$ 226.41  & 54.05 $\pm$ 4.38  & 52.13 $\pm$ 18.29  & 984.68 $\pm$ 128.21\tabularnewline
\hline 
SVM  & 87.6 $\pm$ 0.04  & 248.76 $\pm$ 27.49  & 732.64 $\pm$ 260.56  & 43.37 $\pm$ 2.35  & 53.47 $\pm$ 6.29  & 6169.24 $\pm$ 281.49\tabularnewline
\hline 
MLP	& 88.01 $\pm$ 0.11	& 350.99 $\pm$ 185.53	& 730.93 $\pm$ 374.84	& 61.64 $\pm$ 33.61	& 56.33 $\pm$ 31.6	& 7014.06 $\pm$ 110.095 \tabularnewline
\hline 
\end{tabular}
}
\end{table*}

@@

\begin{table*}
\centering{}%
\caption{Predicting Total sales for all publishers based on features selected
by each method. Best values in bold.
\label{tab:results_all_publishers_fs}}
% RELIEFATTRIBUTEEVAL
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
\hline 
kNN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
\hline 
RF &  \textbf{91.0 $\pm$0.05} &  \textbf{198.16 $\pm$19.50} &  \textbf{589.35 $\pm$195.80} &  \textbf{34.61 $\pm$2.27} &  \textbf{44.21 $\pm$11.63} & 3.63 $\pm$0.20\\
\hline 
LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
\hline 
SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
\hline  
MLP	& 88.58 $\pm$ 0.09	& 384.94 $\pm$ 342.05	& 769.74 $\pm$ 427.35	& 67.47 $\pm$ 60.6	& 58.71 $\pm$ 34.81	& 4.9 $\pm$ 0.047\\
\hline

\end{tabular}
}
% CFSSUBEVAL
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
\hline
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
\hline 
kNN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
\hline 
RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
\hline 
LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
\hline 
SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
\hline
MLP	& 87.26 $\pm$ 0.1	& 420.02 $\pm$ 491.51	& 771.6 $\pm$ 514.03	& 73.6 $\pm$ 87.04	& 60.09 $\pm$ 46.83	& 1.08 $\pm$ 0.019\\
\hline
\end{tabular}
}
% SOM
\centering{}% SOM
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{SOM}}\tabularnewline
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  & 86.6 $\pm$0.10  & 234.09 $\pm$23.19  & 699.56 $\pm$317.20  & 40.92 $\pm$3.25  & 53.70 $\pm$26.87  & 0.475 $\pm$0.12\tabularnewline
\hline 
kNN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  &  \textbf{0.001 $\pm$0.004}\tabularnewline
\hline 
RF &  \textbf{89.8 $\pm$0.05}  &  \textbf{211.87 $\pm$20.07}  &  \textbf{617.78 $\pm$187.16}  &  \textbf{37.02 $\pm$2.46}  &  \textbf{46.58 $\pm$11.14}  & 2.93 $\pm$0.11\tabularnewline
\hline 
LR  & 85.5 $\pm$0.08  & 351.99 $\pm$23.72  & 714.76 $\pm$214.21  & 61.65 $\pm$4.28  & 54.67 $\pm$16.88  & 0.01 $\pm$0.01\tabularnewline
\hline 
SVM  & 84.5 $\pm$0.04  & 267.71 $\pm$33.82  & 888.33 $\pm$308.93  & 46.60 $\pm$2.87  & 64.62 $\pm$5.45  & 32.27 $\pm$4.74\tabularnewline
\hline 
MLP	& 84.3 $\pm$ 0.12	& 388.79 $\pm$ 274.18	& 851.01 $\pm$ 422.03	& 68.26 $\pm$ 49.64	& 65.85 $\pm$ 36.49	& 3.29 $\pm$ 0.042\tabularnewline
\hline
\end{tabular}
}
\end{table*}

@@

\begin{table*}
\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company). Best values in bold. }
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  &  \textbf{90.0 $\pm$0.10} &  \textbf{670.24 $\pm$181.05}  &  \textbf{1065.34 $\pm$413.84}  &  \textbf{40.83 $\pm$10.86}  &  \textbf{43.56 $\pm$19.87}  & 0.03 $\pm$0.002\tabularnewline
\hline 
kNN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  &  \textbf{0 $\pm$0.0001}\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
MLP	& 84.42 $\pm$ 0.12	& 1105.61 $\pm$ 445.66	& 1776.68 $\pm$ 1148.31	& 66.52 $\pm$ 23.63	& 70.41 $\pm$ 41.88	& 1.65 $\pm$ 0.008 \tabularnewline
\hline
\end{tabular}
}
\label{Table:case1results}
\end{table*}

\begin{table*}
\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company). Best values in bold. }
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
kNN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
\hline 
RF &  \textbf{85.8 $\pm$0.17}  & 14.19 $\pm$6.69  &  \textbf{23.57 $\pm$11.83}  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  &  \textbf{14.01 $\pm$7.61}  & 25.61 $\pm$15.30  &  \textbf{40.66 $\pm$16.03}  &  \textbf{53.28 $\pm$18.45}  & 0.02 $\pm$0.02\tabularnewline
\hline 
MLP	& 71.33 $\pm$ 0.35	& 27.46 $\pm$ 14.59	& 49 $\pm$ 34.83	& 82.5 $\pm$ 38.48	& 108.85 $\pm$ 66.21	& 0.45 $\pm$ 0.004\tabularnewline
\hline
\end{tabular}
}
\label{Table:case2results}
\end{table*}

\begin{table*}
\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  &  \textbf{88.9 $\pm$0.07} &  \textbf{71.26 $\pm$21.29}  &  \textbf{125.19 $\pm$50.09}  &  \textbf{39.25 $\pm$11.77}  &  \textbf{47.50 $\pm$15.93}  & 0.05 $\pm$0.03\tabularnewline
\hline 
kNN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
MLP	& 80.83 $\pm$ 0.12	& 122.8 $\pm$ 56.86	& 207.12 $\pm$ 100.44	& 67.13 $\pm$ 31.38	& 78.14 $\pm$ 39.92	& 2.83 $\pm$ 0.012\tabularnewline
\hline
\end{tabular}
}
\label{Table:case3results}
\end{table*}
